Overview and Status of Assumptions of Physics\footnote{http://assumptionsofphysics.org} \\ \ifextended (Extended version) \else (Short version) \fi

### 2020-01-13 Articles/Overview/overview.tex
Overview: minor tweaks

\extendedfalse

@@

\title{Overview and Status of Assumptions of Physics\footnote{http://assumptionsofphysics.org} \\
\ifextended (Extended version)
\else (Short version)
\fi}
\author{Gabriele Carcassi, Christine A. Aidala}
\date{November 2019}

@@

\begin{abstract}
	This article gives an overview of the project ``Assumptions of Physics'' which aims to rederive the known laws from a few physically meaningful starting points. It presents the motivations behind the project, a summary of the main findings and current status of the research.	
\end{abstract}

@@

As we plan to update this document, please make sure you have a recent version. Each subsection will be fairly self-contained to allow the reader to skim through the document and focus on the parts of interest. It will contain a summary section at the beginning and a titled paragraph for each of the main idea or finding.

>>>>

\extendedtrue

@@

\title{Overview and Status of Assumptions of Physics\footnote{http://assumptionsofphysics.org} \\
\ifextended (Extended version)
\else (Short version)
\fi}
\author{Gabriele Carcassi, Christine A. Aidala}
\date{January 2020}

@@

\begin{abstract}
	This article gives an informal overview of the project ``Assumptions of Physics'' which aims to rederive the known laws from a few physically meaningful starting points. It presents the motivations behind the project, a summary of the main findings and current status of the research.	
\end{abstract}

@@

As we plan to update this document, please make sure you have a recent version. Each subsection will be fairly self-contained to allow the reader to skim through the document and focus on the parts of interest. It will contain a summary section at the beginning and a titled paragraph for each of the main ideas or findings.
